%-------------------------
% ATS-Optimized Resume in LaTeX (One Page)
% Author : Sankalp Rajeev
%-------------------------

\documentclass[letterpaper,11pt]{article}

% ---------- Packages ----------
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% ---------- Page Style & Margin ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.15in}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

% ---------- Section Formatting ----------
\titleformat{\section}{\vspace{-2pt}\scshape\large}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]
\pdfgentounicode=1

% ---------- Custom Commands ----------
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}
{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2\\\textit{\small #3} & \textit{\small #4}\\\end{tabular*}\vspace{-6pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, label={\small$\bullet$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textbf{#1} & #2\\\end{tabular*}\vspace{-6pt}}

% -----------------------------------------
\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\Huge \textbf{Sankalp Rajeev}}\\[4pt]
    Dearborn, MI $\vert$ (480) 208-2139 $\vert$ \href{mailto:srajeev@umich.edu}{srajeev@umich.edu} $\vert$ \href{https://www.linkedin.com/in/sankalp-rajeev/}{LinkedIn} $\vert$ \href{https://github.com/sankalp-rajeev}{GitHub} $\vert$ \href{https://sankalp-rajeev.onrender.com/}{Portfolio}
\end{center}

% ---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{University of Michigan – Dearborn}{Sep 2024 -- Dec 2026}{M.Sc., Artificial Intelligence \& M.S.E., Robotics Engineering; \textit{GPA 3.90/4.00}}{Dearborn, MI}
    \resumeSubheading{Arizona State University}{Aug 2020 -- May 2024}{B.S., Computer Science; Minor: Mathematical Concepts of Engineering \textit{GPA 3.71/4.00}}{Tempe, AZ}
\resumeSubHeadingListEnd

% ---------- WORK EXPERIENCE ----------
\section{Work Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Zoetis}{May 2025 -- Nov 2025}{AI Micro Tools Developer Intern}{Kalamazoo, MI}
    \resumeItemListStart
        \resumeItem{Engineered Streamlit micro-tools to automate and enhance SDLC documentation for a regulated GxP environment.}
        \resumeItem{Developed multi-stage ETL pipelines and integrated corporate LLM APIs for automated classification, trend analysis, and decision support across ServiceNow datasets.}
        \resumeItem{Architected and delivered a real-time analytics dashboard, including its custom SQL-backed data pipeline, to track tool adoption, accelerating documentation workflows and saving an estimated $\sim$1,000 engineer-hours annually.}
    \resumeItemListEnd

    \resumeSubheading{Mistral Solutions Pvt Ltd}{Jun 2024 -- Aug 2024}{AI/ML Engineer Intern}{Bangalore, India}
    \resumeItemListStart
      \resumeItem{Deployed and optimized YOLOv8 models on a resource-constrained Mistral EagleKit (Qualcomm QRB5165) to perform real-time object detection, enabling autonomous route monitoring for heavy-payload, high-altitude UAVs.}
      \resumeItem{Refactored Lua-based AHRS and obstacle avoidance logic; integrated Qualcomm SNPE SDK with mixed-precision quantization, cutting compute latency 25\%.}
    \resumeItemListEnd


    \resumeSubheading{Astroseed}{Aug 2023 -- May 2024}{Software Developer}{Tempe, AZ}
    \resumeItemListStart
        \resumeItem{Led Agile sprints and backlog reprioritization, coordinating cross-functional collaboration across engineering teams.}
        \resumeItem{Architected the perception pipeline by integrating a 3D depth camera with a YOLOv5 model in ROS.}
        \resumeItem{Implemented SLAM-based autonomous navigation in Gazebo for path planning and obstacle avoidance.}
    \resumeItemListEnd

    \resumeSubheading{Machani Robotics}{Jun 2022 -- Aug 2022}{Software Development Engineering Intern}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Developed 6-DOF robotic-arm control software via CAN protocol for real-time motion planning.}
        \resumeItem{Built autonomous drawing task execution system with TDD, integrated with a ROS vision pipeline (Python/C++) and 3D depth camera for object recognition.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% ---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\href{https://github.com/sankalp-rajeev/meetingsmindAI}{MeetingMind AI} (Python, FastAPI, React, Docker, GCP)}{Dec 2025 -- Jan 2026}
    \resumeItemListStart
        \resumeItem{Architected a 5-phase ML pipeline orchestrating Whisper (ASR), Pyannote (diarization), YOLOv11 (face detection), and Gemini (LLM) to generate speaker-attributed meeting transcripts with automated summaries and action items.}
        \resumeItem{Integrated Gemini Vision (VLM) for multimodal slide/chart extraction, and engineered a speaker-face matching algorithm using IoU-based tracking with cosine similarity on 512-dim ArcFace embeddings.}
        \resumeItem{Deployed a RAG system (LangChain, ChromaDB, Vertex AI) with FastAPI backend and React frontend on Google Cloud Run via Docker containers.}
    \resumeItemListEnd

\resumeProjectHeading{\href{https://github.com/sankalp-rajeev/Carla-Autonomous-Vehicle}{Autonomous Driving Systems in CARLA} (Python, PyTorch)}{Jan 2025 -- Apr 2025}
  \resumeItemListStart
    \resumeItem{Developed a real-time 3D trajectory mapping system by engineering a visual SLAM pipeline that fused stereo camera and IMU sensor data for localization and mapping.}
    \resumeItem{Implemented a PPO-based RL agent with CNN-encoded semantic features in a custom CARLA Gym environment, integrating YOLOv8 and UFLD for perception-driven lane adherence and obstacle avoidance.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

% ---------- SKILLS ----------
\section{Skills}
 \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \small \textbf{Languages} & \small Python, C/C++, SQL, JavaScript, Java, Lua, MATLAB \\
  \small \textbf{Frameworks \& Libraries} & \small PyTorch, TensorFlow, FastAPI, React, LangChain, HuggingFace, ROS, OpenCV, scikit-learn \\
  \small \textbf{Cloud/DevOps} & \small Docker, Git, GCP (Cloud Run, Vertex AI), Azure \\
  \small \textbf{Domains} & \small Generative AI, NLP, Computer Vision, Reinforcement Learning, Full-Stack Development, MLOps \\
 \end{tabular*}

\end{document}
